
\documentclass[oneside]{ausarbeitung}
\bibliography{latexlit}


% ----------------------------------------------------------------------

\begin{document}

%--- Sprachauswahl
% Erlaubte Werte:
%   \selectlanguage{english}
%   \selectlanguage{ngerman}
\selectlanguage{english}

%--- Art der Arbeit
% Erlaubte Werte:
%   \Praxissemesterbericht
\Projektbericht
%   \Bachelorarbeit
%   \Seminararbeit
%   \Masterarbeit

%--- Studiengang:
% Erlaubte Werte:
%   \Informatik
%   \Elektronik
%   \DataScience
\Informatik

\title{Epidemics}

\author{Sascha Mößle, Tim Staudenmaier}
\matrikelnr{75987, 75981}

%--- Ist der Erstbetreuer (\examinerA) an der Hochschule ein Professor?
% Erlaubte Werte:
%   \examinerIsAProfessortrue   % Ja
%   \examinerIsAProfessorfalse  % Nein
\examinerIsAProfessortrue   % Ja

%--- Betreuer
\examinerA{Prof.~Dr.~Thomas~Thierauf}
%\examinerB{Prof.~Dr.~Ulrich~Klauck}

%--- Einreichungsdatum
\date{14.3.2023}

%--- Angaben zur Firma
% Auskommentieren, wenn die Arbeit nicht bei einer ext. Firma gemacht wurde.
%\companyname{Beispielfirma}
%\industrialsector{Beispielbranche}
%\department{Beispielabteilung}
%\companystreet{Beispielstr. 1}
%\companycity{12345 Musterstadt}

%--- Angaben zum Betreuer bei dieser Firma
%\advisorname{Name des Betreuers}
%\advisorphone{(01234) 567-890}
%\advisoremail{name@company.xxx}

%--- Titelseite Anzeigen
\maketitle
\cleardoublepage

%---
\pagenumbering{roman}
\setcounter{page}{1}

%--- Firmendaten Anzeigen
% Auskommentieren, wenn die Arbeit nicht bei einer ext. Firma gemacht wurde.
%\makeworkplace
%\cleardoublepage

%--- Eidesstattliche Erklärung anzeigen
\makeaffirmation
\cleardoublepage

%---
\begin{abstract}
 Epidemic diseases are an important area of studies. During the history of humans there
 were multiple instances of epidemics singificantly affecting large parts of the world.
 One recent example would be the Corona virus which brought most parts of the world to a 
 standstill. The area of epidemics focuses on such contagious diseases which spread from
 person to person, like Corona of influenza.

 Depending on the characteristics of the virus epidemics can have a very different progression.
 Some may explosively affect the whole world while not causing many casualties while others
 spread very slowly but linger for a long time with a high fatality rate. An important 
 part of studying these diseases is simulating how different diseases could affect the world.
 The simulation of such diseases can be accomplished using network graphs. This paper introduces
 a model wich can be used for simulation and explains how the program that allows to simulate
 a disease using that model is built.
\end{abstract}
%-----------------------------------------------------------------------
\cleardoublepage
\tableofcontents

%---
\listoffigures

%---


\cleardoublepage
\pagenumbering{arabic}
\setcounter{page}{1}

\algrenewcommand\algorithmicrequire{\textbf{Input:}}
\algrenewcommand\algorithmicensure{\textbf{Output:}}

% ----------------------------------------------------------------------

\chapter{Introduction}
\label{cha:introduction}
\input{tex/introduction}

\chapter{Theory of modeling epidemics}
\label{cha:general_principles}
\input{tex/general_principles}

\chapter{Implementation}
\label{cha:implementation}
\input{tex/imp_general}

\chapter{Network Generation}
\label{cha:network_generation}
\input{tex/imp0_graph_generation}

\chapter{Network Display}
\label{cha:network_display}
\input{tex/imp1_graph_display}

\chapter{Visual Simulation}
\label{cha:visual_simulation}
\input{tex/imp2_simulation}

\chapter{Experiments}
\label{cha:experiments}
\input{tex/experiments}

\chapter{Summary and Outlook}
\label{cha:summary}
\input{tex/summary}

% \chapter{Introduction}
% \label{cha:introduction}
% \input{tex/introduction}

% \chapter{Terminology}
% \label{cha:terminology}
% \input{tex/terminology}

% \chapter{Defining different types of Games}
% \label{cha:gameDefinitions}
% \input{tex/gameDefinitions}

% \chapter{Solution Strategies and Nash Equilibria}
% \label{cha:solutionStrategies}
% \input{tex/solutionStrategies}

% \chapter{Complexity of finding Nash equilibria}
% \label{cha:complexityOfFindingNash}
% \input{tex/complexityOfFindingNash}

% \chapter{Summary}
% \label{cha:summary}
% \input{tex/summary}

%-----------------------------------------------------------------------
\appendix

%---
\printbibliography[heading=bibintoc]

\end{document}